---
title: "Adv R Homework 1"
author: "Suman Bhattacharjee (22200484)"
format: 
  pdf:
    embed-resources: true
    page-layout: full
    code-block-bg: "#e5e6eb"
    fontsize: 9 pt
    geometry:
      - right=22mm
      - left=22mm
      - top=28mm
      - bottom=28mm
include-in-header:
  text: |
   \usepackage{authblk,amsmath}
editor: visual
fig-width: 7
fig-height: 3
---

# Introduction

For this homework we will use the **'USArrests'** dataset which is present in r. This dataset contains the crime rates (murder, assault, rape) and percentage urban population of each state in the US.

# Summary

First let us look at the general summaries of the variables of this dataset

```{r}
#| echo: false

library(datasets) # Loading the library

summary(USArrests)
```

We can see that on average, assault is a more common crime in US than rape and murder. States can have an assault rate as high as 337 assaults per 100,000 population.

# Plot

Now we will try to see how the rate of assault is related to the percentage urban population of a state. To do this we will use a scatter plot and visualize the relation.

```{r}
#| echo: false # For hiding the code in the render
#| message: false # For hiding any messages and warnings
#| warning: false
library(ggplot2)

# Plotting the data using base R
ggplot(data = USArrests, aes(x=UrbanPop, y = Assault))+
  geom_point(color = 'brown')+
  labs(x='% Urban Population', y = 'Assault rate', 
       title = 'Assault Rate vs Percentage of Urban Population')+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_smooth(method = "lm", se = FALSE, color = "orange")

```

# Insight

As we can see from the above scatter plot, there is a **positive linear correlation** between the Assault rate (per 100,000) and the percentage urban population.
